Analyzing Sakura Flowering Trends Under Climate Change

### 2024-12-02 paper/paper.qmd
check render ability

>>>>

```{r}
#| label: fig-flowering-distribution
#| fig-cap: Distribution of Sakura Flowering Dates
#| warning: false 
#| message: false
#| fig-align: center

plot_flowering_distribution <- ggplot(clean_sakura_data, aes(x = day_of_year)) +
  geom_histogram(binwidth = 5, fill = "steelblue", color = "black") +
  labs(
    title = "Distribution of Sakura Flowering Dates",
    x = "Day of Year (Flowering Date)",
    y = "Frequency"
  ) +
  theme_minimal()

print(plot_flowering_distribution)
```
